Notes on 10d Super Yang-Mills

### 2019-03-20 10d_SYM_Notes.tex
Computations in the abelian case
Added comments on Baulieu's scalar supersymmetry

%\addbibresource{Twist.bib}

@@

\section{Baulieu's 10 Model}

The ordinary fields $A$ and $\lambda$ of super Yang-Mills will decompose according to the decomposition of the vector and Weyl spinor representations of $\SO(10)$ into irreducible $\SU(5)$-representations.  So, explicitly $A$ splits up into fields
\[A_{1,0} + A_{0,1} \in \Omega^{1,0}(\CC^5; \gg) \oplus \Omega^{0,1}(\CC^5; \gg),\]
and $\lambda$ splits up into fields
\[\chi + \psi + B \in \Pi(\Omega^0(\CC^5; \gg) \oplus \Omega^{1,0}(\CC^5; \gg) \oplus \Omega^{0,2}(\CC^5; \gg)).\]
In terms of these fields, and including the auxiliary field $h$, the action functional becomes
\[S(A_{1,0}, A_{0,1}, \chi, \psi, B, h) = \int \langle (B \wedge \ol \dd_{A_{0,1}} B) + J^2(F_{2, 0}\wedge F_{0,2})\Omega + \|h\|^2\Omega + h J(F_{1,1}) \Omega + J( \chi \wedge (\ol \dd_{A_{0,1}} \psi)) \Omega + J^2(B \wedge (\dd_{A_{1,0}} \psi)) \Omega \rangle.\]
One derives this action functional by decomposing the 10d super Yang-Mills action functional into $\SU(5)$ irreducible component fields, then introducing a Lagrange multiplier $h$ to eliminate the $F_{1,1}^2$ term.
%SU(5) BRST and BV Fields, Action Functional, BV Complex

\subsection{Off-Shell Action of a Scalar Supersymmetry}
%Does it do anything interesting to the anti-fields?

\brian{I realized I'm still confused with the role of Baulieu's $h$-field. 
I really suspect it's different than the usual auxiliary field story. 
It seems like Baulieu doesn't even write down the apparent off-shell SUSY module structure. 
}
\brian{I think without ever introducing an auxiliary field we can obtain the following module structure.}

@@

@@

%\pagestyle{bib}
%\printbibliography

>>>>

\newcommand{\brian}[1]{\textcolor{blue}{BW: #1}}

\addbibresource{Twist.bib}

@@

\subsection{An Off-Shell Supersymmetry Action?}
\brian{I realized I'm still confused with the role of Baulieu's $h$-field. 
I really suspect it's different than the usual auxiliary field story. 
It seems like Baulieu doesn't even write down the apparent off-shell SUSY module structure. 
}
\brian{I think without ever introducing an auxiliary field we can obtain the following module structure.}

@@

\subsubsection{Abelian case}

The BV differential is
\begin{align*}
\delta_{BV} c &= 0 \\
\delta_{BV} A &= \d c \\
\delta_{BV} \lambda &= 0 \\
\delta_{BV} \lambda^* &= \sd D_A \lambda \\
\delta_{BV} A^* &= \d\ast F \\
\delta_{BV} c^* &= \d A^*
\end{align*}

\[I^{(1)} = \int (\lambda^*, \sd F \epsilon) + \int A^* \Gamma(\epsilon, \lambda)\]

\[\delta_{BV} I^{(1)} = \int (\sd D_A\lambda, \sd F\epsilon) + \int (\d\ast F) \Gamma(\epsilon, \lambda).\]
\section{Baulieu's 10 Model}

The ordinary fields $A$ and $\lambda$ of super Yang-Mills will decompose according to the decomposition of the vector and Weyl spinor representations of $\SO(10)$ into irreducible $\SU(5)$-representations.  So, explicitly $A$ splits up into fields
\[A_{1,0} + A_{0,1} \in \Omega^{1,0}(\CC^5; \gg) \oplus \Omega^{0,1}(\CC^5; \gg),\]
and $\lambda$ splits up into fields
\[\chi + \psi + B \in \Pi(\Omega^0(\CC^5; \gg) \oplus \Omega^{1,0}(\CC^5; \gg) \oplus \Omega^{0,2}(\CC^5; \gg)).\]
In terms of these fields, and including the auxiliary field $h$, the action functional becomes
\[S(A_{1,0}, A_{0,1}, \chi, \psi, B, h) = \int \langle J^2(F_{2, 0}\wedge F_{0,2})\Omega - \frac 12 \|h\|^2\Omega + h J(F_{1,1}) \Omega - J( \chi \wedge (\ol \dd_{A_{0,1}} \psi)) \Omega - J^2(B \wedge (\dd_{A_{1,0}} \psi) - (B \wedge \ol \dd_{A_{0,1}} B)) \Omega \rangle.\]
One derives this action functional by decomposing the 10d super Yang-Mills action functional into $\SU(5)$ irreducible component fields, then introducing a Lagrange multiplier $h$ to eliminate the $F_{1,1}^2$ term.
%SU(5) BRST and BV Fields, Action Functional, BV Complex

\subsection{Off-Shell Action of a Scalar Supersymmetry}

Consider the following square-zero supersymmetry acting on Baulieu's theory:
\begin{align*}
\delta A_{1,0} &= \psi \\
\delta \chi &= h \\
\delta B &= F_{0,2} \\
\end{align*}
acting trivially on all other (BRST) fields.  This clearly squares to zero, so defines an action of the supergroup $\Pi \CC$ on the BRST complex.  We can calculate the variation of the action functional with respect to this symmetry, and see that it vanishes.  Indeed,
\begin{align*}
\delta S &= \int \delta \langle J^2(F_{2, 0}\wedge F_{0,2})\Omega - \frac 12 \|h\|^2\Omega + h J(F_{1,1}) \Omega - J( \chi \wedge (\ol \dd_{A_{0,1}} \psi)) \Omega - J^2(B \wedge (\dd_{A_{1,0}} \psi) - (B \wedge \ol \dd_{A_{0,1}} B)) \Omega \rangle \\
&= \int \langle J^2(\dd_{A_{1,0}} B \wedge F_{0,2})\Omega - 0 + h J(\ol \dd_{A_{0,1}} \psi) \Omega - J( h (\ol \dd_{A_{0,1}} \psi)) \Omega - J^2(F_{0,2} \wedge (\dd_{A_{1,0}} \psi) - 0) \Omega \rangle \\
&= 0.
\end{align*}
This should mean that the $\Pi \CC$ action is off-shell, so extends to an action on the full BV complex (the above calculation should be equivalent to showing that $\delta$ commutes with the BV differential).

@@

\pagestyle{bib}
\printbibliography
